\textbf{AprilTrack: A Particle-Filter based AprilTag Tracker}

### 2017-01-09 paper/paper.tex
Working on paper

Visual tracking of fiducial markers (or fiducials) plays an important role in many robotics and computer vision related fields, including augmented and virtual reality, visual odometry, and object tracking. Due to these scenarios taking place in tructured indoors environments where illumination is often limited, long exposure times to compensate for the reduced lighting produce blurred images, especially when taken from a mobile platform such as quadrotor.

 The majority of previous literature in fiducial detection and monocular object tracking has been focused single-frame fiducial detection. A common assumption in these algorithms is that the image being processed is blur free, expectation which breaks down in empirical situations. For instance, the widely-used AprilTag [cite] marker and its successor, the AprilTag 2 [cite], rely on strong gradients between the tag's background and the surrounding white border to detect the tag. As shown in figure \ref{fig:blurred_tag}, oftentimes such algorithms fail to detect tags that have been blurred, either missing them entirely or discarding them as false positives as the identifying characteristics are completely blurred (for AprilTags this consists of a 6x6 binary grid in the center of the tag).

>>>>

Visual tracking of fiducial markers (or simply fiducials) plays an important role in many robotics and computer vision related fields and applications, including augmented and virtual reality, visual odometry, and object tracking in 6 degrees of freedom (DOF). However, as many of these applications involve the of fiducials in structured indoors environments where illumination is often limited, long exposure times to compensate for the reduced lighting produce blurred images, especially when taken from a mobile platform such as quadrotor.

 The majority of previous literature in fiducial detection has been focused single-frame fiducial detection. A common assumption in these algorithms is that the image being processed is blur free, expectation which breaks down in empirical situations. For instance, the widely-used AprilTag [cite] marker and its successor, the AprilTag 2 [cite], rely on strong gradients between the tag's background and the surrounding white border to detect the tag. As shown in figure \ref{fig:blurred_tag}, oftentimes such algorithms fail to detect tags that have been blurred, either missing them entirely or discarding them as false positives as the identifying characteristics are completely blurred (for AprilTags this consists of a 6x6 binary grid in the center of the tag).
